Analysis

### 2017-03-23 Analysis.Rmd
Reorder factors and add new graphs; update analysis

## Leaf Sheath Blight Severity Model
```{r}
(LShB_lmm_2015 <- lmer(LShB_rating ~ WMGT * NRTE + (1 | REP/WMGT),
                       data = AUDPS_2015))
summary(LShB_lmm_2015)

plot(LShB_lmm_2015)
qqnorm(resid(LShB_lmm_2015))

@@

## Tiller Sheath Blight Severity Model
```{r}
(TShB_lmm_2015 <- lmer(TShB_rating ~ WMGT * NRTE + (1 | REP/WMGT),
                       data = AUDPS_2015))
summary(TShB_lmm_2015)

@@

## Leaf Sheath Blight Severity Model
```{r}
(LShB_lmm_2016 <- lmer(LShB_rating ~ WMGT * NRTE + (1 | REP/WMGT),
                       data = AUDPS_2016))
summary(LShB_lmm_2016)

@@

## Tiller Sheath Blight Severity Model
```{r}
(TShB_lmm_2016 <- lmer(TShB_rating ~ WMGT * NRTE + (1 | REP/WMGT),
                       data = AUDPS_2016))
summary(TShB_lmm_2016)

>>>>

## Leaf Sheath Blight Severity Model
```{r}

# 2015 model goes here

@@

## Tiller Sheath Blight Severity Model
```{r}
TShB_lmm_2015 <- lmer(TShB_AUDPS ~ WMGT * NRTE + (1 | REP/WMGT),
                      data = AUDPS_2015,
                      REML = FALSE)
summary(TShB_lmm_2015)

@@

## Leaf Sheath Blight Severity Model
```{r}
LShB_lmm_2016 <- lmer(LShB_AUDPS ~ WMGT * NRTE + (1 | REP/WMGT),
                      data = AUDPS_2016,
                      REML = FALSE)
summary(LShB_lmm_2016)

@@

## Tiller Sheath Blight Severity Model
```{r}
TShB_lmm_2016 <- lmer(TShB_AUDPS ~ WMGT * NRTE + (1 | REP/WMGT),
                      data = AUDPS_2016,
                      REML = FALSE)
summary(TShB_lmm_2016)
